% !Mode:: "TeX:Hard:UTF-8"
% 2021.02.28 修改原文档部分内容
\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[openany]{ctexrep}
\usepackage{fancyvrb}
\usepackage{cprotect}
\usepackage[T1]{fontenc}
%\renewcommand\rmdefault{ptm}
\usepackage{hyperref}
\hypersetup{colorlinks,%
            linkcolor=red}

\usepackage[centering,top=2.75cm,bottom=2.75cm,right=2.7cm,left=2.7cm]{geometry}

%\setmainfont{Times New Roman}
%===设置本站支持的中文字体==中文字体下载：https://www.latexstudio.net/fonts/font.zip 方正字体勿商用=====
%\setCJKmainfont{Source Han Serif CN}
%[
%  UprightFont = *-Regular,
%  BoldFont = *-Bold,
%  ItalicFont = *-Regular,
%  BoldItalicFont = *-Bold
%]
%\setCJKsansfont{Noto Sans CJK SC}
%[
%  UprightFont = *-Regular,
%  BoldFont = *-Bold,
%  ItalicFont = *-Regular,
%  BoldItalicFont = *-Bold
%]
%\setCJKmonofont{Noto Sans Mono CJK SC}
%[
%  UprightFont = *-Regular,
%  BoldFont = *-Bold,
%  AutoFakeSlant = 0.2
%]

%===========================================================================

\ctexset{
chapter ={
%break = {},
format =\centering\bfseries\zihao{-2},
beforeskip={-10pt plus .2ex minus -.2ex},
afterskip={15pt plus 3pt minus 3pt}},
section = {
format=\raggedright\bfseries\zihao{3},numberformat =\rmfamily,
beforeskip={2ex},
afterskip={2ex plus 3pt minus 3pt}
},}

\usepackage[listings,breakable,skins]{tcolorbox}
\tcbset{breakable,enhanced,
  skin=bicolor,
  boxrule=0.4pt,
  colframe=NavyBlue,
  colback=NavyBlue!5!White,
  frame style={%
    left color=NavyBlue,
    right color=NavyBlue},
  colbacklower=white,
  }
\newtcblisting{listing}{
  sidebyside
}

\usepackage{xurl}

\usepackage{hologo,amsmath,amsxtra,amscd}
\DeclareMathOperator{\xxx}{xxx}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

\newcommand{\pkg}[1]{\textsf{#1}}
\newcommand\TikZ{\textrm{Ti}\textit{k}\textrm{Z}}
\begin{document}

\begin{titlepage}
\vspace*{5\baselineskip}
 {\hfill\huge\bfseries   amsmath 宏包中文使用手册}

 {\hfill\LARGE\itshape  User's Guide For the amsmath Package}\\[-5pt]%
    \noindent\rule{\linewidth}{.4pt}\\[-5pt]
  \noindent{\color{gray}\rule{\linewidth}{10.4pt}}\\[-15pt]
  \noindent\rule{\linewidth}{.4pt}  \par \vskip .5\baselineskip
  \begin{flushright}%
  译者：向禹 \ 老师\\
  Email: 739049687@qq.com\\
   {\today}%
  \end{flushright}%
  \vfill
  \vfill
  \begin{flushleft}%、
     \url{https://www.latexstudio.net}
  \end{flushleft}%
 \clearpage
\end{titlepage}

\tableofcontents
%\end{shaded}

\input{intro.tex}

\input{packagepar.tex}

\input{displayequation.tex}

\input{mathfeatures.tex}

\input{Operatornames.tex}

\input{textcommand.tex}

\input{integralandsum.tex}

\input{Commutativediagrams.tex}

\input{mathfont.tex}


\addcontentsline{toc}{chapter}{参考文献}
\begin{thebibliography}{2}
\bibitem{1} George Gr\"atzer, \emph{More Math into \LaTeX}, fifth ed., Springer, New York, 2016.
\bibitem{2} Donald E.Knuth, \emph{The \TeX book}, Addison-Wesley, Reading, MA, 1984.
\bibitem{3} Leslie Lamport, \emph{\LaTeX: A document preparation system}, 2nd revised ed., Addison-Wesley, Reading, MA, 1994.
\bibitem{4} Frank MittelBach, Michel Goossens, et al., \emph{The \LaTeX companion}, second ed., Addison-Wesley, Reading, MA, 2004. This is now also available as an ebook, in both English and German; see \url{http://www.latex-project.org/help/books}.
\bibitem{5} Frank Mitterlbach and Rainer Sch\"opf, \emph{The new font family selection——user interface to standard \LaTeX, TUGboat} \textbf{11}, no. 2(June 1990), pp. 297-305.
\bibitem{6} Michael Spivak, \emph{The joy of \TeX}, 2nd revised ed., Amer. Math. Soc., Providence, RI, 1990.
\bibitem{7} \emph{AMS author handbook}, seperate versions for journal articles, monographs and proceedings articles, Amer. Math. Soc., Providence, RI, 2017; \url{https://www.ams.org/publications/authors/tex/author-handbook}.
\bibitem{8}\emph{AMSFonts version} 2.2d——\emph{user's guide}, Amer. Math. Soc., Provindence, RI, 2002; distributed with the AMSFonts package \url{http://mirror.ctan.org/tex-archive/fonts/amsfonts/doc/amsfndoc.pdf}.
\bibitem{9}\emph{Using the} {\bfseries amsmath} \emph{package}, version 2.20.3, Amer. Math. Soc., Provindence, RI,2017; \url{http://mirror.ctan.org/tex-archive/macros/latex/required/amscls/doc/amsthdoc.pdf}
\bibitem{10}Morten Hogholm, Lars Masden, \emph{The} {\bfseries mathtools} \emph{package}, 2018;
\url{http://mirror.ctan.org/tex-archive/macros/latex/contrib/mathtools/mathtools.pdf}.
\bibitem{11}The \LaTeX Project, \url{https://www.latex-project.org/}
.
\bibitem Online discussion group comp.text.tex, \url{https://groups.google.com/forum/\#!forum/comp.text.tex}
    .
\bibitem{13}Online question and answer forum {\bfseries tex.stackexchange},
\url{https://tex.stackexchange.com/}.
\end{thebibliography}

\end{document} 